---
title: "Star Digital Analysis"
author: "Huiyin(Cloris) He"
date: "3/22/2021"
output: 
  html_document:
    toc: True
    toc_float:
      collapsed: false
      smooth_scroll: false
---
### Part 1. Online Advertising effectiveness

```{r,include=FALSE}
####read data####
star=read.csv('~/Documents/UCI/3. WINTER/BANA 277. CUST & SOCIAL ANLYT/assignment 3. star digital/star_digital.csv')
```

* Run a t-test to make sure that the difference in mean of the two groups are the same, indicating that the experimental setup is unbiased.
  + H0 : difference in mean = 0, the setup in the of control and test groups are the same
  + HA : difference in mean != 0, the setup in the of control and test groups are different

```{R}
####1. online advertising effectiveness####
  #sum up the impressions
star$Timp=rowSums(star[4:9])
  ##t-test####
control=star[star$test==0,]
test=star[star$test==1,]
  #check if they have the same variance
var(control$purchase)
var(test$purchase) #same variance
  #t-test
t.test(control$Timp,test$Timp,var.equal = TRUE)
```

With a p-value of 0.8918, we could not reject the null hypothesis, therefore concluding the two group setups are the same and we could proceed with further analysis.

We split the data into control and test group and then built a logistic regression model with independent variable: purchase, dependent variable: test

```{r}
  #model####
model=glm(purchase~ test,
          data=star, family=binomial())
summary(model) #seems to have a positive effect
```

We assume the level of significance to be 0.1 because our case is in a business context. Since the p-value of the variable ‘test’ is 0.0614 which is less than 0.1, the variable “test” is statistically significant which indicates that exposing consumers to Star ads has a positive effect on purchasing the package.

### Part 2. Frequency effect of advertising on purchase

```{r}
####2. frequency effect####

  ####model including interaction terms####
model2=glm(purchase~Timp*test,data=star,family = binomial())
summary(model2) #positive effect

  #exponential of coefficients
exp(model2$coefficients) 
  #odds of test group
exp(model2$coefficients[2]+model2$coefficients[3]+model2$coefficients[4])#increases the odds by 1.76%
  #odds of control group
exp(model2$coefficients[2]) #increases the odds by 1.6%
```

In the test group, with one unit increase in impression, there will be 1.76% increases in the chance of purchasing.

In the control group, with every additional unit increase in impression, there will be 1.60% increases in the chance of purchasing.

While the two numbers seem to be very close, the test group is still slightly higher than the control group on increasing the odds of purchasing. Thus, we can conclude that increasing the frequency of advertising will increase the probability of purchasing.

### Part 3. Conversion effectiveness of site 1-5 vs. site 6

```{R}
####3. which site to advertise on ####

  ####model with interaction terms####
#sum of site 1-5
star$imp_15=rowSums(star[4:8])
model3=glm(purchase~imp_15+imp_6+imp_15*test+imp_6*test,data=star,family = binomial())
summary(model3)

  #site1-5:test
model3$coefficients
exp(model3$coefficients[2]+model3$coefficients[4]+model3$coefficients[5]) #increases the odds by 2.84%
  #site1-5:control
exp(model3$coefficients[2]) #increases the odds by 1.96%
  #site6:test
exp(model3$coefficients[3]+model3$coefficients[4]+model3$coefficients[6]) #increases the odds by 1.14%
  #site6:control
exp(model3$coefficients[3]) #increases the odds by 0.40%
```

For site 1-5:
1.028376 is the odds of purchasing in the test group for sites 1-5. So for the test group, increasing 1 unit of impression increases the odds of purchasing by 2.84% on site 1-5.

For site 6:
1.011439 is the odds of purchasing in the test group for site 6. So for the test group, increasing 1 unit of impression increases the odds of purchasing by 1.14% on site 6.

Thus, we can conclude that ads on site 1-5 are more effective in terms of conversion than site 1-5 since the increase of odds of purchasing for site 1-5 is more than site 6.

### Part 4. ROI
From Part 3, we found out that site 1-5 is more effective. For this part, we will take the cost of the ads on each website into account to determine which one has a better ROI.

Since there is an oversampling issue in our dataset, we have an issue with the biased estimate of the constant term. We included the following offset value in our model to recover the term.

Population conversion rate=0.00153; 
Sample conversion rate=0.50

```{r}
# 4. ROI ####
  # model w/ offset ####
model4=glm(purchase~imp_15+imp_6+imp_15*test+imp_6*test,
           offset =rep(log(((1-0.00153)/0.00153)/((1-0.5)/0.5)),nrow(star)),
           data=star,family = binomial())
summary(model4)
```

The cost of advertising at Site 1-5 is 25 dollars per thousand impressions and the cost of advertising at Site 6 is 20 dollars per thousand impressions. And a purchase results in a lifetime contribution of 1,200 dollars for Star Digital.

Next, we calculated ROI for both sites.

```{r}
  #calculate the ROI ####
  #site 1-5
new=data.frame(imp_15=1,imp_6=0,test=1)
predict15=predict.glm(model4,new,type='response')[1]
predict15 *1200 /25

  #site 6
new2=data.frame(imp_15=0,imp_6=1,test=1)
predict6=predict.glm(model4,new2,type = 'response')[1]
predict6*1200/20
```

From the above comparison, we can see that site 6 has a higher ROI than site 1-5 and thus, Star Digital should put its advertising budget on site 6.
